---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AgreementPhi

<!-- badges: start -->
[![R-CMD-check](https://github.com/giuseppealfonzetti/AgreementPhi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/giuseppealfonzetti/AgreementPhi/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/giuseppealfonzetti/AgreementPhi/graph/badge.svg)](https://app.codecov.io/gh/giuseppealfonzetti/AgreementPhi)
<!-- badges: end -->

The `AgreementPhi` package is the companion of "Alfonzetti G., Bellio R., Vidoni P. *Accurate agreement estimation in crowdsourced relevance assessments*". It allows the accurate estimation of the general $\Phi$ agreement measure among multiple crowd-workers assessing a given collection of items (Checco et al. 2017).

## Installation

You can install `AgreementPhi` using the `devtools` package:

``` r
devtools::install_github("giuseppealfonzetti/AgreementPhi")
```

## Example

Generate a synthetic dataset with continuous ratings in (0,1)

```{r}
library(AgreementPhi)
set.seed(321)
items <- 200
budget_per_item <- 8
alphas <- runif(items, -2, 2)
agr <- .8

dt <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  DATA_TYPE = "continuous",
  ALPHA = alphas
)
```

Prepare the data with `rating_data()`, which validates the input and reports diagnostics

```{r}
rd <- rating_data(dt$rating, dt$id_item, dt$id_worker)
```

Fit the model using `agreement()`

```{r}
fit <- agreement(rd, METHOD = "modified", NUISANCE = c("items"), VERBOSE = TRUE)
```

Construct confidence intervals

```{r}
ci <- confint(fit)
ci
```

# References
 - Checco A., Roitero K., Maddalena E., Mizzaro S., Demartini G., (2017). “Let’s Agree to Disagree: Fixing Agreement Measures for Crowdsourcing.” *Proceedings of the AAAI Conference on Human Computation and Crowdsourcing* **5**: 11–20. [doi](https://doi.org/10.1609/hcomp.v5i1.13306)


