---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AgreementPhi

<!-- badges: start -->
[![R-CMD-check](https://github.com/giuseppealfonzetti/AgreementPhi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/giuseppealfonzetti/AgreementPhi/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/AgreementPhi)](https://CRAN.R-project.org/package=AgreementPhi)

<!-- badges: end -->

The `AgreementPhi` package allows to accurately estimate the general agreement among raters across a collection of items. It provides a general tool to deal with percentage and ordinal data.

## Installation

You can install `AgreementPhi` using the `devtools` package:

``` r
devtools::install_github("giuseppealfonzetti/AgreementPhi")
```

## Example

Generate a synthetic dataset with continuous ratings in (0,1)

```{r generate data}
library(AgreementPhi)
set.seed(123)

# setting dimension
items <- 100 
budget_per_item <- 10
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  DATA_TYPE = "continuous",
  SEED = 123
)
```

We fit the model on the continuous ratings data and compare the agreement estimated between diffferent methods

```{r fit continuous}
# fit via profile likelihood
fit_c_p <- agreement(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  METHOD = "profile",
  VERBOSE = TRUE)
fit_c_p$pl_agreement

# fit via modified profile likelihood
fit_c_mp <- agreement(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_c_mp$mpl_agreement
```

We can plot the relative loglikelihood profiles

```{r}
rll <- get_rll(fit_c_mp, PLOT = TRUE)
```

and also construct confidence intervals for the estimated agreement

```{r}
get_ci(fit_c_mp)$agreement_ci
```

Consider now ratings collected on Likert-type rating. To allow for a direct comparison with the previous dataset, we directly discretise the continuous ratings generated previously

```{r discretise}
rating_k3 <- cont2ord(dt$rating, K=3)
rating_k6 <- cont2ord(dt$rating, K=6)
```

Now, we evaluate the agreement on the discretised data. The fitting function automatically detects the ordinal ratings scale.

```{r fit ordinal}
fit_k3_p <- agreement(
  RATINGS = rating_k3,
  ITEM_INDS = dt$id_item,
  METHOD = "profile")
fit_k3_p$pl_agreement

fit_k3_mp <- agreement(
  RATINGS = rating_k3,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_k3_mp$mpl_agreement

fit_k6_p <- agreement(
  RATINGS = rating_k6,
  ITEM_INDS = dt$id_item,
  METHOD = "profile")
fit_k6_p$pl_agreement

fit_k6_mp <- agreement(
  RATINGS = rating_k6,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_k6_mp$mpl_agreement


```

Also in case of ordinal data we can plot the profiles of the relative log-likelihoods


```{r}
rll <- get_rll(fit_k6_mp, PLOT = TRUE)
```

and construct confidence intervals


```{r}
get_ci(fit_k3_mp)$agreement_ci
get_ci(fit_k6_mp)$agreement_ci
```

### TWO-WAY ####

Consider data generated according to the two-way model. Fitting a one-way specification will likely result in underestimating the agreement

```{r}
set.seed(123)

# setting dimension
items <- 100 
budget_per_item <- 10
workers <- 100
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)
betas <- c(0, runif(workers-1, -1, 1))
# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_twoway <- sim_data(
  J = items,
  B = budget_per_item,
  W = workers,
  AGREEMENT = agr,
  ALPHA = alphas,
  BETA = betas,
  DATA_TYPE = "continuous",
  SEED = 123
)

# estimation via oneway specification
fit_c_oneway <- agreement(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  METHOD = "modified",
  MODEL = "oneway",
  VERBOSE = TRUE)

# estimation via twoway specification
fit_c_twoway <- agreement(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  MODEL = "twoway",
  VERBOSE = TRUE)

# estimation via twoway specification | ordinal data
tictoc::tic()
fit_k6_twoway <- agreement(
  RATINGS = cont2ord(dt_twoway$rating, K=6),
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  MODEL = "twoway",
  VERBOSE = TRUE)
tictoc::toc()

tictoc::tic()
fit_k6_oneway <- agreement(
  RATINGS = cont2ord(dt_twoway$rating, K=6),
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  MODEL = "oneway",
  VERBOSE = TRUE)
tictoc::toc()
```

Consider now data generated according to the one-way model. Fitting one-way and two-way specifications will likely result in similar estimates of the agreement.

```{r}
set.seed(123)

# setting dimension
items <- 100
budget_per_item <- 10
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_oneway <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  W=50,
  DATA_TYPE = "continuous",
  SEED = 123
)

# estimation via oneway specification
fit_c_oneway <- agreement(
  RATINGS = dt_oneway$rating,
  ITEM_INDS = dt_oneway$id_item,
  METHOD = "modified",
  MODEL = "oneway",
  VERBOSE = TRUE)

# estimation via twoway specification
fit_c_twoway <- agreement(
  RATINGS = dt_oneway$rating,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  MODEL = "twoway",
    # CONTROL = list(PROF_MAX_ITER=10),
  VERBOSE = TRUE)

# estimation via twoway specification | ordinal data
tictoc::tic()
fit_k6_twoway <- agreement(
  RATINGS = cont2ord(dt_oneway$rating, K=6),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  MODEL = "twoway",
  VERBOSE = TRUE)
tictoc::tic()

set.seed(1)
thr <- sort(runif(5))
ratingk <- cont2ord(dt_oneway$rating, K=6, TRESHOLDS=thr)
unique_rates <- sort(unique(ratingk))
rates_map <- setNames(seq_along(unique_rates), unique_rates)
ratingk <- as.numeric(rates_map[as.character(ratingk)])

tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()

tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  TAU_START = c(0, thr, 1),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()
```






```{r}
# setting dimension
items <- 100 
budget_per_item <- 10
workers <- 100
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)
betas <- c(0, runif(workers-1, -1, 1))
# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_twoway <- sim_data(
  J = items,
  B = budget_per_item,
  W = workers,
  AGREEMENT = agr,
  ALPHA = alphas,
  BETA = betas,
  DATA_TYPE = "continuous",
  SEED = 123
)

tictoc::tic()
fit_twoway <- agreement2(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "workers"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()

# tictoc::tic()
# fit_old <- agreement(
#   RATINGS = dt_twoway$rating,
#   ITEM_INDS = dt_twoway$id_item,
#   METHOD = "modified",
#   MODEL = "oneway",
#   VERBOSE = TRUE)
# tictoc::toc()
tictoc::tic()
fit_oneway <- agreement2(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  # BETA_START = rep(-.5, workers-1),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()
tictoc::tic()
fit_twoway <- agreement2(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "workers"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()
tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = cont2ord(dt_twoway$rating, K=6),
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "workers"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 20,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()

# tictoc::tic()
# fit_old <- agreement(
#   RATINGS = cont2ord(dt_twoway$rating, K=6),
#   ITEM_INDS = dt_twoway$id_item,
#   METHOD = "modified",
#   MODEL = "oneway",
#   VERBOSE = TRUE)
# tictoc::toc()

tictoc::tic()
fit_oneway <- agreement2(
  RATINGS = cont2ord(dt_twoway$rating, K=6),
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  # BETA_START = rep(-2, workers-1),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()
```


Non equispaced


```{r}
set.seed(123)

# setting dimension
items <- 200
budget_per_item <- 10
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_oneway <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  W=50,
  DATA_TYPE = "continuous",
  SEED = 123
)

init_tau <- function(y, K) {
    counts <- tabulate(factor(y, levels = seq_len(K)), nbins = K)
    cum_p <- cumsum(counts) / sum(counts)
    c(0, cum_p[-K], 1)
  }
set.seed(1)

K <- 6
thr <- sort(runif(K-1))
ratingk <- cont2ord(dt_oneway$rating, K=K, TRESHOLDS=thr)
unique_rates <- sort(unique(ratingk))
rates_map <- setNames(seq_along(unique_rates), unique_rates)
ratingk <- as.numeric(rates_map[as.character(ratingk)])
table(ratingk)
init_tau(y=ratingk, K=K)

# Profiled thresholds
tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "profile",
  NUISANCE = c("items", "workers", "thresholds"),
  # CONTROL = list(
  #   SEARCH_RANGE = 10,
  #   MAX_ITER = 10,
  #   PROF_SEARCH_RANGE = 5,
  #   PROF_MAX_ITER = 20,
  #   ALT_MAX_ITER = 20,
  #   ALT_TOL = 1e-4
  # ),
  VERBOSE = TRUE)
fit_k6_twoway$profile$agreement
tictoc::toc()

# Fixed empirical
tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "profile",
  NUISANCE = c("items", "workers"),
  # CONTROL = list(
  #   SEARCH_RANGE = 10,
  #   MAX_ITER = 100,
  #   PROF_SEARCH_RANGE = 5,
  #   PROF_MAX_ITER = 10,
  #   ALT_MAX_ITER = 10,
  #   ALT_TOL = 1e-2
  # ),
  VERBOSE = TRUE)
fit_k6_twoway$profile$agreement
tictoc::toc()

# Fixed true locations
tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "profile",
  NUISANCE = c("items", "workers"),
  TAU_START = c(0, thr, 1),
  # CONTROL = list(
  #   SEARCH_RANGE = 10,
  #   MAX_ITER = 100,
  #   PROF_SEARCH_RANGE = 5,
  #   PROF_MAX_ITER = 10,
  #   ALT_MAX_ITER = 10,
  #   ALT_TOL = 1e-2
  # ),
  VERBOSE = TRUE)
fit_k6_twoway$profile$agreement
tictoc::toc()

# Fixed empirical
tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  # CONTROL = list(
  #   SEARCH_RANGE = 10,
  #   MAX_ITER = 100,
  #   PROF_SEARCH_RANGE = 5,
  #   PROF_MAX_ITER = 10,
  #   ALT_MAX_ITER = 10,
  #   ALT_TOL = 1e-2
  # ),
  VERBOSE = TRUE)
fit_k6_twoway$profile$agreement
tictoc::toc()

# Fixed true
K <- 6
thr <- seq(0,1, by=1/K)
thr[2:(K)] <- thr[2:(K)] + runif(K-1, -1e-1, 1e-1)
thr
tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = cont2ord(dt_oneway$rating, K=K, TRESHOLDS=thr[2:(K)]),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  # TAU_START = seq(0,1,by=1/K),
  TAU_START = thr,
  # CONTROL = list(
  #   SEARCH_RANGE = 10,
  #   MAX_ITER = 100,
  #   PROF_SEARCH_RANGE = 5,
  #   PROF_MAX_ITER = 10,
  #   ALT_MAX_ITER = 10,
  #   ALT_TOL = 1e-2
  # ),
  VERBOSE = TRUE)
fit_k6_twoway$profile$agreement
tictoc::toc()


```