---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AgreementPhi

<!-- badges: start -->
[![R-CMD-check](https://github.com/giuseppealfonzetti/AgreementPhi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/giuseppealfonzetti/AgreementPhi/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/AgreementPhi)](https://CRAN.R-project.org/package=AgreementPhi)

<!-- badges: end -->

The `AgreementPhi` package allows to accurately estimate the general agreement among raters across a collection of items. It provides a general tool to deal with percentage and ordinal data.

## Installation

You can install `AgreementPhi` using the `devtools` package:

``` r
devtools::install_github("giuseppealfonzetti/AgreementPhi")
```

## Example

Generate a synthetic dataset with continuous ratings in (0,1)

```{r generate data}
library(AgreementPhi)
set.seed(123)

# setting dimension
items <- 100 
budget_per_item <- 10
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items)

# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  DATA_TYPE = "continuous",
  SEED = 123
)
```

We fit the model on the continuous ratings data and compare the agreement estimated between diffferent methods

```{r fit continuous}
# fit via profile likelihood
fit_c_p <- agreement(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  METHOD = "profile")
fit_c_p$pl_agreement

# fit via modified profile likelihood
fit_c_mp <- agreement(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_c_mp$mpl_agreement
```

We can plot the relative loglikelihood profiles

```{r}
rll <- get_rll(fit_c_mp, PLOT = TRUE)
```

and also construct confidence intervals for the estimated agreement

```{r}
get_ci(fit_c_mp)$agreement_ci
```

Consider now ratings collected on Likert-type rating. To allow for a direct comparison with the previous dataset, we directly discretise the continuous ratings generated previously

```{r discretise}
rating_k3 <- cont2ord(dt$rating, K=3)
rating_k5 <- cont2ord(dt$rating, K=5)
rating_k7 <- cont2ord(dt$rating, K=7)
```

Now, we evaluate the agreement on the discretised data. The fitting function automatically detects the ordinal ratings scale.

```{r fit ordinal}
fit_k3_p <- agreement(
  RATINGS = rating_k3,
  ITEM_INDS = dt$id_item,
  METHOD = "profile")
fit_k3_p$pl_agreement

fit_k3_mp <- agreement(
  RATINGS = rating_k3,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_k3_mp$mpl_agreement

fit_k5_p <- agreement(
  RATINGS = rating_k5,
  ITEM_INDS = dt$id_item,
  METHOD = "profile")
fit_k5_p$pl_agreement

fit_k5_mp <- agreement(
  RATINGS = rating_k5,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_k5_mp$mpl_agreement

fit_k7_p <- agreement(
  RATINGS = rating_k7,
  ITEM_INDS = dt$id_item,
  METHOD = "profile")
fit_k7_p$pl_agreement

fit_k7_mp <- agreement(
  RATINGS = rating_k7,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_k7_mp$mpl_agreement

```

Also in case of ordinal data we can plot the profiles of the relative log-likelihoods


```{r}
rll <- get_rll(fit_k3_mp, PLOT = TRUE)
```

and construct confidence intervals


```{r}
get_ci(fit_k3_mp)$agreement_ci
get_ci(fit_k7_mp)$agreement_ci
```

