---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AgreementPhi

<!-- badges: start -->
[![R-CMD-check](https://github.com/giuseppealfonzetti/AgreementPhi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/giuseppealfonzetti/AgreementPhi/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/AgreementPhi)](https://CRAN.R-project.org/package=AgreementPhi)

<!-- badges: end -->

The `AgreementPhi` package allows to accurately estimate the general agreement among raters across a collection of items. It provides a general tool to deal with percentage and ordinal data.

## Installation

You can install `AgreementPhi` using the `devtools` package:

``` r
devtools::install_github("giuseppealfonzetti/AgreementPhi")
```

## Example

Generate a synthetic dataset with continuous ratings in (0,1)

```{r generate data}
library(AgreementPhi)
set.seed(123)

# setting dimension
items <- 100 
budget_per_item <- 10
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  DATA_TYPE = "continuous",
  SEED = 123
)
```

We fit the model on the continuous ratings data and compare the agreement estimated between diffferent methods

```{r fit continuous}
# fit via profile likelihood
fit_c_p <- agreement(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  METHOD = "profile",
  VERBOSE = TRUE)
fit_c_p$pl_agreement

# fit via modified profile likelihood
fit_c_mp <- agreement(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_c_mp$mpl_agreement
```

We can plot the relative loglikelihood profiles

```{r}
rll <- get_rll(fit_c_mp, PLOT = TRUE)
```

and also construct confidence intervals for the estimated agreement

```{r}
get_ci(fit_c_mp)$agreement_ci
```

Consider now ratings collected on Likert-type rating. To allow for a direct comparison with the previous dataset, we directly discretise the continuous ratings generated previously

```{r discretise}
rating_k3 <- cont2ord(dt$rating, K=3)
rating_k6 <- cont2ord(dt$rating, K=6)
```

Now, we evaluate the agreement on the discretised data. The fitting function automatically detects the ordinal ratings scale.

```{r fit ordinal}
fit_k3_p <- agreement(
  RATINGS = rating_k3,
  ITEM_INDS = dt$id_item,
  METHOD = "profile")
fit_k3_p$pl_agreement

fit_k3_mp <- agreement(
  RATINGS = rating_k3,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_k3_mp$mpl_agreement

fit_k6_p <- agreement(
  RATINGS = rating_k6,
  ITEM_INDS = dt$id_item,
  METHOD = "profile")
fit_k6_p$pl_agreement

fit_k6_mp <- agreement(
  RATINGS = rating_k6,
  ITEM_INDS = dt$id_item,
  METHOD = "modified")
fit_k6_mp$mpl_agreement


```

Also in case of ordinal data we can plot the profiles of the relative log-likelihoods


```{r}
rll <- get_rll(fit_k6_mp, PLOT = TRUE)
```

and construct confidence intervals


```{r}
get_ci(fit_k3_mp)$agreement_ci
get_ci(fit_k6_mp)$agreement_ci
```

### TWO-WAY ####

Consider data generated according to the two-way model. Fitting a one-way specification will likely result in underestimating the agreement

```{r}
set.seed(123)

# setting dimension
items <- 100 
budget_per_item <- 10
workers <- 100
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)
betas <- c(0, runif(workers-1, -1, 1))
# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_twoway <- sim_data(
  J = items,
  B = budget_per_item,
  W = workers,
  AGREEMENT = agr,
  ALPHA = alphas,
  BETA = betas,
  DATA_TYPE = "continuous",
  SEED = 123
)

# estimation via oneway specification
fit_c_oneway <- agreement(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  METHOD = "modified",
  MODEL = "oneway",
  VERBOSE = TRUE)

# estimation via twoway specification
fit_c_twoway <- agreement(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  MODEL = "twoway",
  VERBOSE = TRUE)

# estimation via twoway specification | ordinal data
tictoc::tic()
fit_k6_twoway <- agreement(
  RATINGS = cont2ord(dt_twoway$rating, K=6),
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  MODEL = "twoway",
  VERBOSE = TRUE)
tictoc::toc()

tictoc::tic()
fit_k6_oneway <- agreement(
  RATINGS = cont2ord(dt_twoway$rating, K=6),
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  MODEL = "oneway",
  VERBOSE = TRUE)
tictoc::toc()
```

Consider now data generated according to the one-way model. Fitting one-way and two-way specifications will likely result in similar estimates of the agreement.

```{r}
set.seed(123)

# setting dimension
items <- 100
budget_per_item <- 10
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_oneway <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  W=50,
  DATA_TYPE = "continuous",
  SEED = 123
)

# estimation via oneway specification
fit_c_oneway <- agreement(
  RATINGS = dt_oneway$rating,
  ITEM_INDS = dt_oneway$id_item,
  METHOD = "modified",
  MODEL = "oneway",
  VERBOSE = TRUE)

# estimation via twoway specification
fit_c_twoway <- agreement(
  RATINGS = dt_oneway$rating,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  MODEL = "twoway",
    # CONTROL = list(PROF_MAX_ITER=10),
  VERBOSE = TRUE)

# estimation via twoway specification | ordinal data
tictoc::tic()
fit_k6_twoway <- agreement(
  RATINGS = cont2ord(dt_oneway$rating, K=6),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  MODEL = "twoway",
  VERBOSE = TRUE)
tictoc::tic()

set.seed(1)
thr <- sort(runif(5))
ratingk <- cont2ord(dt_oneway$rating, K=6, TRESHOLDS=thr)
unique_rates <- sort(unique(ratingk))
rates_map <- setNames(seq_along(unique_rates), unique_rates)
ratingk <- as.numeric(rates_map[as.character(ratingk)])

tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()

tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  TAU_START = c(0, thr, 1),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()
```






```{r}
# setting dimension
items <- 100 
budget_per_item <- 10
workers <- 100
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)
betas <- c(0, runif(workers-1, -1, 1))
# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_twoway <- sim_data(
  J = items,
  B = budget_per_item,
  W = workers,
  AGREEMENT = agr,
  ALPHA = alphas,
  BETA = betas,
  DATA_TYPE = "continuous",
  SEED = 123
)

tictoc::tic()
fit_twoway <- agreement2(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "workers"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()

# tictoc::tic()
# fit_old <- agreement(
#   RATINGS = dt_twoway$rating,
#   ITEM_INDS = dt_twoway$id_item,
#   METHOD = "modified",
#   MODEL = "oneway",
#   VERBOSE = TRUE)
# tictoc::toc()
tictoc::tic()
fit_oneway <- agreement2(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  # BETA_START = rep(-.5, workers-1),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()
tictoc::tic()
fit_twoway <- agreement2(
  RATINGS = dt_twoway$rating,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "workers"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()
tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = cont2ord(dt_twoway$rating, K=6),
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "workers"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 20,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()

# tictoc::tic()
# fit_old <- agreement(
#   RATINGS = cont2ord(dt_twoway$rating, K=6),
#   ITEM_INDS = dt_twoway$id_item,
#   METHOD = "modified",
#   MODEL = "oneway",
#   VERBOSE = TRUE)
# tictoc::toc()

tictoc::tic()
fit_oneway <- agreement2(
  RATINGS = cont2ord(dt_twoway$rating, K=6),
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  # BETA_START = rep(-2, workers-1),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 100,
    PROF_SEARCH_RANGE = 5,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-2
  ),
  VERBOSE = TRUE)
tictoc::toc()
```


Non equispaced one way


```{r}
set.seed(321)

# setting dimension
items <- 50
budget_per_item <- 10
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .4

# generate continuous rating in (0,1)
dt_oneway <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  W=50,
  DATA_TYPE = "continuous",
  SEED = 123
)

init_tau <- function(y, K) {
    counts <- tabulate(factor(y, levels = seq_len(K)), nbins = K)
    cum_p <- cumsum(counts) / sum(counts)
    c(0, cum_p[-K], 1)
  }
set.seed(1)

K <- 6
thr <- sort(runif(K-1))
thr
ratingk <- cont2ord(dt_oneway$rating, K=K, TRESHOLDS=thr)
unique_rates <- sort(unique(ratingk))
rates_map <- setNames(seq_along(unique_rates), unique_rates)
ratingk <- as.numeric(rates_map[as.character(ratingk)])
table(ratingk)
init_tau(y=ratingk, K=K)

# Profiled thresholds
# tictoc::tic()
# fit_k6_twoway <- agreement2(
#   RATINGS = ratingk,
#   ITEM_INDS = dt_oneway$id_item,
#   WORKER_INDS = dt_oneway$id_worker,
#   METHOD = "profile",
#   NUISANCE = c("items", "thresholds"),
#   VERBOSE = TRUE)
# fit_k6_twoway$profile$agreement
# tictoc::toc()

tictoc::tic()
fit_k6_profiled <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "thresholds"),
  # CONTROL = list(
  #   SEARCH_RANGE = 10,
  #   MAX_ITER = 20,
  #   PROF_SEARCH_RANGE = 4,
  #   PROF_MAX_ITER = 20,
  #   ALT_MAX_ITER = 20,
  #   ALT_TOL = 1e-4
  # ),
  VERBOSE = TRUE)
tictoc::toc()

# Fixed equispaced
tictoc::tic()
fit_k6_fixed_equi <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  TAU_START = seq(0,1,1/K),
  VERBOSE = TRUE)
# fit_k6_fixed_equi$profile$agreement
tictoc::toc()

# Fixed true
tictoc::tic()
fit_k6_fixed_true <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items"),
  TAU_START = c(0,thr,1),
  VERBOSE = TRUE)
fit_k6_fixed_true$profile$agreement
tictoc::toc()
```


```{r}
set.seed(123)

# setting dimension
items <- 50 
budget_per_item <- 10
workers <- 50
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)
betas <- c(0, runif(workers-1, -1, 1))
# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_twoway <- sim_data(
  J = items,
  B = budget_per_item,
  W = workers,
  AGREEMENT = agr,
  ALPHA = alphas,
  BETA = betas,
  DATA_TYPE = "continuous",
  SEED = 123
)

init_tau <- function(y, K) {
    counts <- tabulate(factor(y, levels = seq_len(K)), nbins = K)
    cum_p <- cumsum(counts) / sum(counts)
    c(0, cum_p[-K], 1)
  }
set.seed(1)

K <- 6
thr <- sort(runif(K-1))
thr
ratingk <- cont2ord(dt_twoway$rating, K=K, TRESHOLDS=thr)
unique_rates <- sort(unique(ratingk))
rates_map <- setNames(seq_along(unique_rates), unique_rates)
ratingk <- as.numeric(rates_map[as.character(ratingk)])
table(ratingk)
init_tau(y=ratingk, K=K)

# # Profiled thresholds
# tictoc::tic()
# fit_k6_twoway <- agreement2(
#   RATINGS = ratingk,
#   ITEM_INDS = dt_twoway$id_item,
#   WORKER_INDS = dt_twoway$id_worker,
#   METHOD = "profile",
#   NUISANCE = c("items", "thresholds"),
#   CONTROL = list(
#     SEARCH_RANGE = 10,
#     MAX_ITER = 10,
#     PROF_SEARCH_RANGE = 4,
#     PROF_MAX_ITER = 10,
#     ALT_MAX_ITER = 10,
#     ALT_TOL = 1e-4
#   ),
#   VERBOSE = TRUE)
# fit_k6_twoway$profile$agreement
# tictoc::toc()

tictoc::tic()
fit_k6_twoway <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "workers", "thresholds"),
  CONTROL = list(
    SEARCH_RANGE = 10,
    MAX_ITER = 10,
    PROF_SEARCH_RANGE = 4,
    PROF_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-4
  ),
  VERBOSE = TRUE)
tictoc::toc()

# Fixed equispaced
tictoc::tic()
fit_k6_twoway_fixed <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_twoway$id_item,
  WORKER_INDS = dt_twoway$id_worker,
  METHOD = "modified",
  NUISANCE = c("items", "workers"),
  TAU_START = seq(0,1,1/K),
  # TAU_START = c(0,thr,1),
  VERBOSE = TRUE)
tictoc::toc()


```


Initialisation



```{r}
set.seed(321)

# setting dimension
items <- 100
budget_per_item <- 10
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .4

# generate continuous rating in (0,1)
dt_oneway <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  W=100,
  DATA_TYPE = "continuous",
  SEED = 123
)

init_tau <- function(y, K) {
    counts <- tabulate(factor(y, levels = seq_len(K)), nbins = K)
    cum_p <- cumsum(counts) / sum(counts)
    c(0, cum_p[-K], 1)
  }
set.seed(1)

K <- 6
thr <- sort(runif(K-1))
thr
ratingk <- cont2ord(dt_oneway$rating, K=K, TRESHOLDS=thr)
unique_rates <- sort(unique(ratingk))
rates_map <- setNames(seq_along(unique_rates), unique_rates)
ratingk <- as.numeric(rates_map[as.character(ratingk)])
table(ratingk)
init_tau(y=ratingk, K=K)

tictoc::tic()
fit_k6_init <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "profile",
  NUISANCE = c("thresholds"),
  ALPHA_START = alphas,
  VERBOSE = TRUE)
tictoc::toc()

tictoc::tic()
fit_k6_profiled <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  METHOD = "profile",
  NUISANCE = c("thresholds", "items"),
  VERBOSE = TRUE)
tictoc::toc()
```






```{r}
validate_params_type(
  NUISANCE = c("items", "workers"),
  TARGET = c("phi", "thresholds"),
  DATA_TYPE="ordinal"
)
```


 Extended profile
```{r}
# setting dimension
items <- 100
budget_per_item <- 10
n_obs <- items * budget_per_item
workers <- 50
# item-specific intercepts to generate the data
alphas <- runif(items, -2, 2)

# true agreement (between 0 and 1)
agr <- .7

# generate continuous rating in (0,1)
dt_oneway <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  W=workers,
  DATA_TYPE = "continuous",
  SEED = 321
)

init_tau <- function(y, K) {
    counts <- tabulate(factor(y, levels = seq_len(K)), nbins = K)
    cum_p <- cumsum(counts) / sum(counts)
    c(0, cum_p[-K], 1)
  }
set.seed(1)

K <- 6
thr <- sort(runif(K-1))
thr
ratingk <- cont2ord(dt_oneway$rating, K=K, TRESHOLDS=thr)
unique_rates <- sort(unique(ratingk))
rates_map <- setNames(seq_along(unique_rates), unique_rates)
ratingk <- as.numeric(rates_map[as.character(ratingk)])
table(ratingk)
init_tau(y=ratingk, K=K)
tau_start <- seq(0,1,by=1/K)

tictoc::tic()
fit_k6_mod_BASE <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  TAU_START = c(0,thr,1),
  METHOD = "modified",
  NUISANCE = c("items", "thresholds"),
  CONTROL = list(
    PROF_SEARCH_RANGE = 1
  ),
  VERBOSE = TRUE)
tictoc::toc()
fit_k6_mod_BASE$alpha
fit_k6_mod_BASE$cpp_args$ALPHA_START
fit_k6_mod_BASE$tau
fit_k6_mod_BASE$cpp_args$TAU_START
alphas
thr
fit_k6_mod_BASE$loglik

tictoc::tic()
fit_k6_mod_fixed <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  TAU_START = c(0,thr,1),
  METHOD = "modified",
  NUISANCE = c("items"),
  CONTROL = list(
    PROF_SEARCH_RANGE = 1
  ),
  VERBOSE = TRUE)
tictoc::toc()

fit_k6_mod_fixed$alpha
fit_k6_mod_fixed$cpp_args$ALPHA_START
fit_k6_mod_fixed$tau
fit_k6_mod_fixed$cpp_args$TAU_START
alphas
thr
fit_k6_mod_fixed$loglik


# Fixed thresholds
cor(fit_k6_mod_fixed$alpha, alphas)

# Profiled thresholds  
cor(fit_k6_mod_BASE$alpha, alphas)

# And show the threshold values side by side
data.frame(
  true = thr,
  profiled = fit_k6_mod_BASE$tau[2:6],
  difference = fit_k6_mod_BASE$tau[2:6] - thr
)



R_neg_prof_ext <- function(
  PAR,
  Y,
  ITEM_INDS,
  WORKER_INDS,
  ALPHA_START,
  BETA_START,
  J,
  W ,
  K,
  ITEMS_NUISANCE,
  WORKER_NUISANCE,
  THRESHOLDS_NUISANCE,
  PROF_SEARCH_RANGE,
  PROF_UNI_MAX_ITER,
  ALT_MAX_ITER,
  ALT_TOL){

    raw_phi <- PAR[1]
    raw_tau <- PAR[2:length(PAR)]
    phi <- exp(raw_phi)
    tau <- raw2tau(raw_tau)
    

    -cpp_profile_likelihood(
      Y = as.numeric(Y),
      ITEM_INDS = ITEM_INDS,
      WORKER_INDS = WORKER_INDS,
      ALPHA_START = ALPHA_START,
      BETA_START = BETA_START,
      TAU_START = tau,
      PHI = phi,
      J = as.integer(J),
      W = as.integer(W),
      K = as.integer(K),
      DATA_TYPE = "ordinal",
      ITEMS_NUISANCE = ITEMS_NUISANCE,
      WORKER_NUISANCE = WORKER_NUISANCE,
      THRESHOLDS_NUISANCE = THRESHOLDS_NUISANCE,
      PROF_SEARCH_RANGE = PROF_SEARCH_RANGE,
      PROF_UNI_MAX_ITER = PROF_UNI_MAX_ITER,
      ALT_MAX_ITER = ALT_MAX_ITER,
      ALT_TOL = ALT_TOL
    )

  }



  R_neg_mod_prof_ext <- function(
    PAR,
    Y,
    ITEM_INDS,
    WORKER_INDS,
    ALPHA_PROF,
    BETA_PROF,
    TAU_MLE,
    PHI_MLE,
    J,
    W ,
    K,
    ITEMS_NUISANCE,
    WORKER_NUISANCE,
    PROF_SEARCH_RANGE,
    PROF_UNI_MAX_ITER,
    ALT_MAX_ITER,
    ALT_TOL)
  {

    raw_phi <- PAR[1]
    raw_tau <- PAR[2:length(PAR)]
    phi <- exp(raw_phi)
    tau <- raw2tau(raw_tau)
    

    -cpp_modified_profile_likelihood_extended(
      Y = as.numeric(Y),
      ITEM_INDS = ITEM_INDS,
      WORKER_INDS = WORKER_INDS,
      ALPHA_MLE = ALPHA_PROF,
      BETA_MLE = BETA_PROF,
      TAU = tau,
      TAU_MLE = TAU_MLE,
      PHI = phi,
      PHI_MLE = PHI_MLE,
      J = as.integer(J),
      W = as.integer(W),
      K = as.integer(K),
      DATA_TYPE = "ordinal",
      ITEMS_NUISANCE = ITEMS_NUISANCE,
      WORKER_NUISANCE = WORKER_NUISANCE,
      PROF_SEARCH_RANGE = PROF_SEARCH_RANGE,
      PROF_UNI_MAX_ITER = PROF_UNI_MAX_ITER,
      ALT_MAX_ITER = ALT_MAX_ITER,
      ALT_TOL = ALT_TOL
    )

  }

tau_raw_start <- tau2raw(c(0, thr, 1))
lower_bounds <- c(log(agr2prec(0.01)), tau_raw_start - 2)
upper_bounds <- c(log(agr2prec(0.99)), tau_raw_start + 2)

# STAGE 1: Coarse optimization with reduced accuracy
cat("Stage 1: Coarse optimization with reduced accuracy...\n")
tictoc::tic()
opt_mle <- optim(
  par = c(log(agr2prec(.5)), tau2raw(tau_start)),
  fn = R_neg_prof_ext,
  Y = as.numeric(ratingk),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  ALPHA_START = rep(0,items),
  BETA_START = rep(0, workers),
  J = items,
  W = workers,
  K = K,
  ITEMS_NUISANCE = TRUE,
  WORKER_NUISANCE = FALSE,
  THRESHOLDS_NUISANCE = FALSE,
  PROF_SEARCH_RANGE = 1,
  PROF_UNI_MAX_ITER = 5,   # Reduced from 10
  ALT_MAX_ITER = 5,         # Reduced from 10
  ALT_TOL = 1e-3,           # Relaxed from 1e-4
  lower = lower_bounds,
  upper = upper_bounds,
  method = "L-BFGS-B",
  control = list(maxit = 50)  # Limit coarse iterations
)
time_coarse <- tictoc::toc()

cat("Stage 1 complete. Agreement:", prec2agr(exp(opt_mle$par[1])), "\n")
cat("Stage 1 thresholds:", raw2tau(opt_mle$par[2:length(opt_mle$par)]), "\n\n")

# STAGE 2: Refinement with full accuracy
cat("Stage 2: Refinement with full accuracy...\n")
tictoc::tic()
opt_mle <- optim(
  par = opt_mle_coarse$par,  # Start from coarse solution
  fn = R_neg_prof_ext,
  Y = as.numeric(ratingk),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  ALPHA_START = rep(0,items),
  BETA_START = rep(0, workers),
  J = items,
  W = workers,
  K = K,
  ITEMS_NUISANCE = TRUE,
  WORKER_NUISANCE = FALSE,
  THRESHOLDS_NUISANCE = FALSE,
  PROF_SEARCH_RANGE = 1,
  PROF_UNI_MAX_ITER = 10,   # Full accuracy
  ALT_MAX_ITER = 10,         # Full accuracy
  ALT_TOL = 1e-4,
  lower = lower_bounds,
  upper = upper_bounds,
  method = "L-BFGS-B",
  control = list(maxit = 50)  # Fewer iterations needed for refinement
)
time_refined <- tictoc::toc()

cat("Stage 2 complete.\n")
cat("Total optimization time:", time_coarse$toc - time_coarse$tic + time_refined$toc - time_refined$tic, "seconds\n")

prec2agr(exp(opt_mle$par[1]))
raw2tau(opt_mle$par[2:length(opt_mle$par)])
c(0,thr,1)
agr


# lambda_hat <- cpp_ordinal_get_lambda2(
#     Y = as.numeric(ratingk),
#     ITEM_INDS = dt_oneway$id_item,
#     WORKER_INDS = dt_oneway$id_worker,
#     ALPHA = rep(0,items),
#     BETA = rep(0, workers),
#     TAU = raw2tau(opt$par[2:length(opt_mle$par)]),
#     PHI = exp(opt_mle$par[1]),
#     J = items,
#     W = workers,
#     K = K,
#     ITEMS_NUISANCE = TRUE,
#     WORKER_NUISANCE = FALSE,
#     THRESHOLDS_NUISANCE = FALSE,
#     PROF_UNI_RANGE = 1,
#     PROF_UNI_MAX_ITER = 100,
#     PROF_MAX_ITER = 100,
#     TOL = 1e-4
# )




# STAGE 1: Coarse modified profile optimization
cat("\nModified Profile Stage 1: Coarse optimization with reduced accuracy...\n")
tictoc::tic()
opt_mp_coarse <- optim(
  par = c(opt_mle$par[1], opt_mle$par[2:length(opt_mle$par)]),
  fn = R_neg_mod_prof_ext,
  Y = as.numeric(ratingk),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  ALPHA_PROF = rep(0,items),
  BETA_PROF = rep(0, workers),
  TAU_MLE = raw2tau(opt_mle$par[2:length(opt_mle$par)]),
  PHI_MLE = exp(opt_mle$par[1]),
  J = items,
  W = workers,
  K = K,
  ITEMS_NUISANCE = TRUE,
  WORKER_NUISANCE = FALSE,
  PROF_SEARCH_RANGE = 1,
  PROF_UNI_MAX_ITER = 5,   # Reduced from 10
  ALT_MAX_ITER = 5,         # Reduced from 10
  ALT_TOL = 1e-3,           # Relaxed from 1e-4
  lower = lower_bounds,
  upper = upper_bounds,
  method = "L-BFGS-B",
  control = list(maxit = 100)
)
time_mp_coarse <- tictoc::toc()

cat("Modified Profile Stage 1 complete. Agreement:", prec2agr(exp(opt_mp_coarse$par[1])), "\n\n")

# STAGE 2: Refinement with full accuracy
cat("Modified Profile Stage 2: Refinement with full accuracy...\n")
tictoc::tic()
opt_mp <- optim(
  par = opt_mp_coarse$par,  # Start from coarse solution
  fn = R_neg_mod_prof_ext,
  Y = as.numeric(ratingk),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  ALPHA_PROF = rep(0,items),
  BETA_PROF = rep(0, workers),
  TAU_MLE = raw2tau(opt_mle$par[2:length(opt_mle$par)]),
  PHI_MLE = exp(opt_mle$par[1]),
  J = items,
  W = workers,
  K = K,
  ITEMS_NUISANCE = TRUE,
  WORKER_NUISANCE = FALSE,
  PROF_SEARCH_RANGE = 1,
  PROF_UNI_MAX_ITER = 10,   # Full accuracy
  ALT_MAX_ITER = 10,         # Full accuracy
  ALT_TOL = 1e-4,
  lower = lower_bounds,
  upper = upper_bounds,
  method = "L-BFGS-B",
  control = list(maxit = 50)
)
time_mp_refined <- tictoc::toc()

cat("Modified Profile Stage 2 complete.\n")
cat("Total modified profile optimization time:", time_mp_coarse$toc - time_mp_coarse$tic + time_mp_refined$toc - time_mp_refined$tic, "seconds\n")

prec2agr(exp(opt_mp$par[1]))
raw2tau(opt_mp$par[2:length(opt_mp$par)])
c(0,thr,1)
agr


# =============================================================================
# UNIVARIATE MODIFIED PROFILE WITH TAU PROFILED AS NUISANCE
# =============================================================================
cat("\n\n=== UNIVARIATE MODIFIED PROFILE (TAU PROFILED) ===\n\n")

# This approach treats tau as nuisance and profiles it out for each phi value
# making the optimization univariate in phi only (much faster!)

R_modified_prof_univariate <- function(
  PHI,
  Y,
  ITEM_INDS,
  WORKER_INDS,
  ALPHA_MLE,
  BETA_MLE,
  TAU_START,
  TAU_MLE,
  PHI_MLE,
  J,
  W,
  K,
  ITEMS_NUISANCE,
  WORKER_NUISANCE,
  PROF_SEARCH_RANGE,
  PROF_UNI_MAX_ITER,
  ALT_MAX_ITER,
  ALT_TOL
) {
  cpp_modified_profile_likelihood_tau_profiled(
    Y = as.numeric(Y),
    ITEM_INDS = ITEM_INDS,
    WORKER_INDS = WORKER_INDS,
    ALPHA_MLE = ALPHA_MLE,
    BETA_MLE = BETA_MLE,
    TAU_START = TAU_START,
    TAU_MLE = TAU_MLE,
    PHI = PHI,
    PHI_MLE = PHI_MLE,
    J = as.integer(J),
    W = as.integer(W),
    K = as.integer(K),
    DATA_TYPE = "ordinal",
    ITEMS_NUISANCE = ITEMS_NUISANCE,
    WORKER_NUISANCE = WORKER_NUISANCE,
    PROF_SEARCH_RANGE = PROF_SEARCH_RANGE,
    PROF_UNI_MAX_ITER = PROF_UNI_MAX_ITER,
    ALT_MAX_ITER = ALT_MAX_ITER,
    ALT_TOL = ALT_TOL
  )
}

# Use MLEs from profile likelihood as starting point
phi_mle <- exp(opt_mle$par[1])
tau_mle <- raw2tau(opt_mle$par[2:length(opt_mle$par)])

# Get the profiled alpha and beta values at the MLE
lambda_mle <- cpp_ordinal_get_lambda2(
  Y = as.numeric(ratingk),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  ALPHA = rep(0, items),
  BETA = rep(0, workers),
  TAU = tau_mle,
  PHI = phi_mle,
  J = items,
  W = workers,
  K = K,
  ITEMS_NUISANCE = TRUE,
  WORKER_NUISANCE = FALSE,
  THRESHOLDS_NUISANCE = FALSE,
  PROF_UNI_RANGE = 1,
  PROF_UNI_MAX_ITER = 10,
  PROF_MAX_ITER = 10,
  TOL = 1e-4
)

alpha_mle <- lambda_mle$alpha
beta_mle <- lambda_mle$beta

cat("Starting univariate modified profile optimization...\n")
cat("Using MLEs: phi =", phi_mle, ", agreement =", prec2agr(phi_mle), "\n")
cat("Thresholds:", tau_mle, "\n")
cat("Alpha (first 5):", head(alpha_mle, 5), "\n")
cat("Beta (first 5):", head(beta_mle, 5), "\n\n")

# First, test the function at the MLE to verify it's working correctly
cat("Testing function at MLE...\n")
ll_at_mle <- R_modified_prof_univariate(
  PHI = phi_mle,
  Y = as.numeric(ratingk),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  ALPHA_MLE = alpha_mle,
  BETA_MLE = beta_mle,
  TAU_START = tau_mle,
  TAU_MLE = tau_mle,
  PHI_MLE = phi_mle,
  J = items,
  W = workers,
  K = K,
  ITEMS_NUISANCE = TRUE,
  WORKER_NUISANCE = FALSE,
  PROF_SEARCH_RANGE = 1,
  PROF_UNI_MAX_ITER = 10,
  ALT_MAX_ITER = 10,
  ALT_TOL = 1e-4
)
cat("Log-likelihood at MLE (phi =", phi_mle, "):", ll_at_mle, "\n\n")

# Test at a few other points to see the function shape
cat("Testing function at several phi values...\n")
test_phis <- c(agr2prec(0.3), agr2prec(0.5), agr2prec(0.68), phi_mle, agr2prec(0.8), agr2prec(0.9))
for (phi_test in test_phis) {
  ll_test <- R_modified_prof_univariate(
    PHI = phi_test,
    Y = as.numeric(ratingk),
    ITEM_INDS = dt_oneway$id_item,
    WORKER_INDS = dt_oneway$id_worker,
    ALPHA_MLE = alpha_mle,
    BETA_MLE = beta_mle,
    TAU_START = tau_mle,
    TAU_MLE = tau_mle,
    PHI_MLE = phi_mle,
    J = items,
    W = workers,
    K = K,
    ITEMS_NUISANCE = TRUE,
    WORKER_NUISANCE = FALSE,
    PROF_SEARCH_RANGE = 1,
    PROF_UNI_MAX_ITER = 10,
    ALT_MAX_ITER = 10,
    ALT_TOL = 1e-4
  )
  cat("  phi =", sprintf("%.4f", phi_test), "(agr =", sprintf("%.4f", prec2agr(phi_test)), "), ll =", sprintf("%.4f", ll_test), "\n")
}
cat("\n")

# Also compare with the regular profile likelihood (without modification)
cat("For comparison, profile likelihood at MLE:\n")
pl_at_mle <- cpp_profile_likelihood(
  Y = as.numeric(ratingk),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  ALPHA_START = alpha_mle,
  BETA_START = beta_mle,
  TAU_START = tau_mle,
  PHI = phi_mle,
  J = items,
  W = workers,
  K = K,
  DATA_TYPE = "ordinal",
  ITEMS_NUISANCE = TRUE,
  WORKER_NUISANCE = FALSE,
  THRESHOLDS_NUISANCE = TRUE,
  PROF_SEARCH_RANGE = 1,
  PROF_UNI_MAX_ITER = 10,
  ALT_MAX_ITER = 10,
  ALT_TOL = 1e-4
)
cat("  Profile LL at MLE:", pl_at_mle, "\n\n")

tictoc::tic()
opt_mp_univariate <- optimize(
  f = R_modified_prof_univariate,
  interval = c(agr2prec(0.01), agr2prec(0.99)),
  maximum = TRUE,
  Y = as.numeric(ratingk),
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  ALPHA_MLE = alpha_mle,
  BETA_MLE = beta_mle,
  TAU_START = tau_mle,  # Use MLE as starting point for tau profiling
  TAU_MLE = tau_mle,
  PHI_MLE = phi_mle,
  J = items,
  W = workers,
  K = K,
  ITEMS_NUISANCE = TRUE,
  WORKER_NUISANCE = FALSE,
  PROF_SEARCH_RANGE = 1,
  PROF_UNI_MAX_ITER = 10,
  ALT_MAX_ITER = 10,
  ALT_TOL = 1e-4
)
time_univariate <- tictoc::toc()

cat("\nUnivariate Modified Profile Results:\n")
cat("Optimal phi:", opt_mp_univariate$maximum, "\n")
cat("Optimal agreement:", prec2agr(opt_mp_univariate$maximum), "\n")
cat("Log-likelihood:", opt_mp_univariate$objective, "\n")
cat("Total time:", time_univariate$toc - time_univariate$tic, "seconds\n")

cat("\n=== COMPARISON ===\n")
cat("Multivariate approach (phi, tau jointly):\n")
cat("  Agreement:", prec2agr(exp(opt_mp$par[1])), "\n")
cat("  Time:", time_mp_coarse$toc - time_mp_coarse$tic + time_mp_refined$toc - time_mp_refined$tic, "seconds\n\n")
cat("Univariate approach (tau profiled):\n")
cat("  Agreement:", prec2agr(opt_mp_univariate$maximum), "\n")
cat("  Time:", time_univariate$toc - time_univariate$tic, "seconds\n")
cat("  Speedup:", (time_mp_coarse$toc - time_mp_coarse$tic + time_mp_refined$toc - time_mp_refined$tic) / (time_univariate$toc - time_univariate$tic), "x\n")

tictoc::tic()
fit_k6_mod <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  # TAU_START = c(0,thr,1),
  TAU_START = raw2tau(opt_mle$par[2:length(opt_mle$par)]),
  # ALPHA_START = lambda_hat$alpha,
  # BETA_START = lambda_hat$beta,
  # PHI_START = exp(opt_mle$par[1]),
  METHOD = "modified",
  NUISANCE = c("items"),
  CONTROL = list(
    PROF_SEARCH_RANGE = 2
  ),
  VERBOSE = TRUE)
tictoc::toc()

tictoc::tic()
fit_k6_mod_BASE <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  # TAU_START = c(0,thr,1),
  TAU_START = raw2tau(opt$par[2:length(opt$par)]),
  PHI_START = exp(opt$par[1]),
  METHOD = "modified",
  NUISANCE = c("items", "thresholds"),
  CONTROL = list(
    PROF_SEARCH_RANGE = 2
  ),
  VERBOSE = TRUE)
tictoc::toc()

tictoc::tic()
fit_k6_mod_BASE <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  # TAU_START = c(0,thr,1),
  TAU_START = tau_start,
  # TAU_START = raw2tau(opt$par[2:length(opt$par)]),
  # PHI_START = exp(opt$par[1]),
  METHOD = "modified",
  NUISANCE = c("items"),
  CONTROL = list(
    PROF_SEARCH_RANGE = 2
  ),
  VERBOSE = TRUE)
tictoc::toc()

agr 
tictoc::tic()
fit_k6_mod_BASE <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  TAU_START = c(0,thr,1),
  METHOD = "modified",
  NUISANCE = c("items", "thresholds"),
  CONTROL = list(
    PROF_SEARCH_RANGE = 2
  ),
  VERBOSE = TRUE)
tictoc::toc()
fit_k6_mod_BASE$alpha
fit_k6_mod_BASE$cpp_args$ALPHA_START
fit_k6_mod_BASE$tau
fit_k6_mod_BASE$cpp_args$TAU_START
alphas
thr

tictoc::tic()
fit_k6_mod_fixed <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  TAU_START = c(0,thr,1),
  METHOD = "modified",
  NUISANCE = c("items"),
  CONTROL = list(
    PROF_SEARCH_RANGE = 2
  ),
  VERBOSE = TRUE)
tictoc::toc()

fit_k6_mod_fixed$alpha
fit_k6_mod_fixed$cpp_args$ALPHA_START
fit_k6_mod_fixed$tau
fit_k6_mod_fixed$cpp_args$TAU_START
alphas
thr
```





```{r}
set.seed(123)
# setting dimension
items <- 100
budget_per_item <- 20
n_obs <- items * budget_per_item
workers <- 100
# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .3

# generate continuous rating in (0,1)
dt_oneway <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  ALPHA = alphas,
  W=workers,
  DATA_TYPE = "continuous",
  SEED = 1
)

init_tau <- function(y, K) {
    counts <- tabulate(factor(y, levels = seq_len(K)), nbins = K)
    cum_p <- cumsum(counts) / sum(counts)
    c(0, cum_p[-K], 1)
  }
set.seed(1)

K <- 6
thr <- sort(runif(K-1))
thr
ratingk <- cont2ord(dt_oneway$rating, K=K, TRESHOLDS=thr)
unique_rates <- sort(unique(ratingk))
rates_map <- setNames(seq_along(unique_rates), unique_rates)
ratingk <- as.numeric(rates_map[as.character(ratingk)])
table(ratingk)
init_tau(y=ratingk, K=K)
tau_start <- seq(0,1,by=1/K)
```


```{r}
# threshold in target
tictoc::tic()
fit_k6_mod_BASE <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  TAU_START = tau_start,
  METHOD = "profile",
  NUISANCE = c("items"),
  TARGET = c("phi", "thresholds"),
  CONTROL = list(
    PROF_MAX_ITER=50,
    PROF_SEARCH_RANGE = 2,
    LBFGS_INVISIBLE = TRUE
  ),
  VERBOSE = TRUE)
tictoc::toc()
fit_k6_mod_BASE[c("loglik", "tau", "profile", "modified")]
```

```{r}
# inited threshold nuisance
tictoc::tic()
fit_k6_nested_profile_1way <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  TAU_START = tau_start,
  METHOD = "profile",
  NUISANCE = c("items", "thresholds"),
  TARGET = c("phi"),
  CONTROL = list(
    PROF_MAX_ITER=50,
    PROF_SEARCH_RANGE = 2,
    LBFGS_INVISIBLE = TRUE,
    LBFGS_MAX_ITERATIONS = 15
  ),
  VERBOSE = TRUE)
tictoc::toc()
fit_k6_nested_profile_1way[c("loglik", "tau", "profile", "modified")]

```

```{r}
tictoc::tic()
fit_k6_nested_mod_profile_1way <- agreement2(
  RATINGS = ratingk,
  ITEM_INDS = dt_oneway$id_item,
  WORKER_INDS = dt_oneway$id_worker,
  TAU_START = tau_start,
  METHOD = "modified",
  NUISANCE = c("items", "thresholds"),
  TARGET = c("phi"),
  CONTROL = list(
    PROF_MAX_ITER=50,
    PROF_SEARCH_RANGE = 2,
    LBFGS_INVISIBLE = TRUE,
    LBFGS_MAX_ITERATIONS = 15
  ),
  VERBOSE = TRUE)
tictoc::toc()
fit_k6_nested_mod_profile_1way[c("loglik", "tau", "profile", "modified")]

```
