---
title: "Intoduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

You can install `AgreementPhi` using the `devtools` package:

``` r
devtools::install_github("giuseppealfonzetti/AgreementPhi")
```

## Basic usage

The `AgreementPhi` package exports a utility function to simulate data by providing the true agreement and item effects. Consider for example to simulate continuous ratings for 200 items, collecting 8 relevance assessments per item, for a total of 1600 responses. We set the true agreement at $\Phi=0.4$

```{r sim_data}
library(AgreementPhi)
set.seed(321)
# setting dimension
items <- 200
budget_per_item <- 8
n_obs <- items * budget_per_item

# item-specific intercepts to generate the data
alphas <- runif(items, -1, 1)

# true agreement (between 0 and 1)
agr <- .4

# generate continuous rating in (0,1)
dt <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  DATA_TYPE = "continuous",
  ALPHA = alphas
)

```

The simulated 1600 ratings are stored in `dt$ratings`, while `dt$id_item` and `dt$id_worker` store the item and worker indices related to each rating

```{r}
names(dt)
head(dt$id_item)
head(dt$id_worker)
head(dt$rating)
length(dt$rating)
```

For convenience, we also provide a plot utility to visualise the data

```{r plot_data, fig.width=7, fig.height=5}
plot_data(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  WORKER_INDS = dt$id_worker
)
```

The core function of the `AgreementPhi` package is `agreement()`, which implements the numerical algorithms to estimate the $\Phi$ agreement via profile and modified profile likelihood methods.
It requires as input the ratings, the item ids and worker ids (specified as integers).
For the estimation via profile likelihood, you can specify `METHOD="profile"`

```{r}
# estimation via profile likelihood
fit_profile <- agreement(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  WORKER_INDS = dt$id_worker,
  NUISANCE = c("items"),
  METHOD = "profile",
  VERBOSE = TRUE)
```

When the `VERBOSE` option is chosen, the function prints on screen some useful information about data dimensions and sparsity. In addition, it also provides an overview of how items and worker effects are treated. In this case, for example, worker effects are considered as constant (set at zero by default), while items effects are profiled out as nuisance parameters. The agreement and precision estimates are available at 

```{r}
fit_profile$profile
```

while the maximum likelihood estimates of the nuisance parameters are available at

```{r}
head(fit_profile$alpha)
```

To use the modified likelihood approach, it is enough to change the `METHOD` argument to `modified`. 

```{r}
# estimation via modified profile likelihood
fit_modified <- agreement(
  RATINGS = dt$rating,
  ITEM_INDS = dt$id_item,
  WORKER_INDS = dt$id_worker,
  NUISANCE = c("items"),
  METHOD = "modified",
  VERBOSE = TRUE)
```

As it can be read from the verbose output, when `METHOD = "modified"`, the proposed algorithm first optimises the profile likelihood to evaluate the maximum likelihood estimators needed to construct the modified profile likelihood. Thus, both estimates can be retrieved from the fitted object

```{r}
fit_modified$profile
fit_modified$modified
```

Once the point estimates are computed, we can draw inference on agreement by using the `get_ci()` function to construct confidence intervals. The function will automatically recognise if the estimates are related to the profile or modified likelihood approach by looking at the fitted object

```{r}
# get standard error and confidence interval
ci_profile <- get_ci(fit_profile)
ci_profile

ci_modified <- get_ci(fit_modified)
ci_modified 
```

For convenience, we provide a utility function to visualise the relative log-likelihood profiles of the two methods as well as the inference results

```{r, fig.width=7, fig.height=5}
# compute log-likelihood over a grid
range_ll <- get_range_ll(fit_modified)

# utility plot function for relative log-likelihood
plot_rll(
  D=range_ll,
  M_EST = fit_modified$modified$agreement,
  P_EST = fit_profile$profile$agreement,
  M_SE = ci_modified$agreement_se,
  P_SE = ci_profile$agreement_se,
  CONFIDENCE=.95
)
```