---
title: "Intoduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r check-algdesign, include=FALSE}
if (!requireNamespace("AlgDesign", quietly = TRUE)) {
  knitr::opts_chunk$set(eval = FALSE)
  message("AlgDesign not installed; vignette chunks will not be evaluated.")
}
```

## Basic usage

The `AgreementPhi` package exports a utility function to simulate data by providing the true agreement and item effects. Consider for example to simulate continuous ratings for 200 items, collecting 8 relevance assessments per item, for a total of 1600 responses. We set the true agreement at $\Phi=0.4$

```{r sim_data}
library(AgreementPhi)
set.seed(321)
items <- 200
budget_per_item <- 8
alphas <- runif(items, -1, 1)
agr <- .4

dt <- sim_data(
  J = items,
  B = budget_per_item,
  AGREEMENT = agr,
  DATA_TYPE = "continuous",
  ALPHA = alphas
)
```

The simulated 1600 ratings are stored in `dt$ratings`, while `dt$id_item` and `dt$id_worker` store the item and worker indices related to each rating

```{r inspect_dt}
names(dt)
head(dt$id_item)
head(dt$id_worker)
head(dt$rating)
length(dt$rating)
```

Use `rating_data()` to validate the input and construct a `rating_data` object. The function reports diagnostics and, for two-way data, supports `plot()`

```{r rating_data}
rd <- rating_data(dt$rating, dt$id_item, dt$id_worker)
```

```{r plot_data, fig.width=7, fig.height=5}
plot(rd)
```

The core function of the `AgreementPhi` package is `agreement()`, which implements the numerical algorithms to estimate the $\Phi$ agreement via profile and modified profile likelihood methods.
It takes a `rating_data` object as its first argument.
For the estimation via profile likelihood, you can specify `METHOD="profile"`

```{r fit_profile}
fit_profile <- agreement(rd, NUISANCE = c("items"), METHOD = "profile", VERBOSE = TRUE)
```

When the `VERBOSE` option is chosen, the function prints on screen some useful information about data dimensions and sparsity. In addition, it also provides an overview of how items and worker effects are treated. In this case, for example, worker effects are considered as constant (set at zero by default), while items effects are profiled out as nuisance parameters. The agreement and precision estimates are available at

```{r profile_estimates}
fit_profile$profile
```

while the maximum likelihood estimates of the nuisance parameters are available at

```{r profile_alpha}
head(fit_profile$alpha)
```

To use the modified likelihood approach, it is enough to change the `METHOD` argument to `modified`.

```{r fit_modified}
fit_modified <- agreement(rd, NUISANCE = c("items"), METHOD = "modified", VERBOSE = TRUE)
```

As it can be read from the verbose output, when `METHOD = "modified"`, the proposed algorithm first optimises the profile likelihood to evaluate the maximum likelihood estimators needed to construct the modified profile likelihood. Thus, both estimates can be retrieved from the fitted object

```{r modified_estimates}
fit_modified$profile
fit_modified$modified
```

Once the point estimates are computed, we can draw inference on agreement by using the `confint()` S3 method to construct confidence intervals. The function will automatically recognise if the estimates are related to the profile or modified likelihood approach by looking at the fitted object

```{r confint}
ci_profile <- confint(fit_profile)
ci_profile

ci_modified <- confint(fit_modified)
ci_modified
```

For convenience, `plot()` visualises the relative log-likelihood profile and confidence interval in one step

```{r plot_fit, fig.width=7, fig.height=5}
plot(fit_modified)
```

If you need the grid data for further analysis, compute it with `get_range_ll()` and pass it back to `plot()` to avoid recomputation

```{r plot_fit_precomputed, fig.width=7, fig.height=5}
range_ll <- get_range_ll(fit_modified)
plot(fit_modified, RANGE_LL = range_ll)
```
