---
title: "Analysing crowdsourced relevance assessments (Roitero et al. 2021)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{roitero2021}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## The data

The `roitero2021` dataset bundled with `AgreementPhi` is a subset of the
crowdsourcing experiment in Roitero et al. (2021), restricted to assessments
collected on the 100-point continuous (S100) relevance scale. Each row is one
worker's `relevance_score` for one `document_id` within a `topic_id`.

```{r load}
library(AgreementPhi)
data(roitero2021)
str(roitero2021)
```

For simplicity, here we focus on a single topic and look at how the related items were assessed.

```{r topic}
topic <- subset(roitero2021, topic_id == 403)
nrow(topic)
```

We retain only workers who "correctly" responded to the gold items
(high-relevance `"H"` above threshold and non-relevant `"N"` below threshold) and
then keep only non-gold items.

```{r filter}

select_workers <- intersect(
  unique(topic[topic$relevance_score > 75 & topic$gold == "H", ]$unit_id),
  unique(topic[topic$relevance_score < 25 & topic$gold == "N", ]$unit_id)
)

topic <- subset(topic, unit_id %in% select_workers & gold == "null")
nrow(topic)
```


As scores wer collected on a 0–100 scale, we map them onto `[0,1]` by simply dividing by 100. To build a `rating_data` object we use the `rating_data()` function.
Since exact 0s and 100s are present in the data, the function automatically detects the inflated beta ratings.

```{r rating_data}
ratings <- topic$relevance_score / 100
items <- as.integer(factor(topic$document_id))
rd <- rating_data(ratings, items)
rd
```

As printed, the checks detected two degenerate items. These correspond to documents where the same value is given by all raters

```{r}
degen_docs <- levels(factor(topic$document_id))[rd$degen_ids]
d <- subset(topic, document_id %in% degen_docs, select = c(document_id, relevance_score))
d[order(d$document_id), ]
```



## Fitting the agreement model

The inflated interval model is a one-way model: the item effects are profiled
out as nuisance parameters. The argument `METHOD = "modified"` uses the modified profile likelihood as objective function to optimize

```{r fit}
fit <- agreement(rd, NUISANCE = "items", METHOD = "modified")
```

We can extract coefficients with the familiar `coef()` method

```{r}
coef(fit)[1:10]
```

where alphas for degenrate items are reported with infinite values

```{r}
coef(fit)[paste0("alpha_", rd$degen_ids)]
```


## Confidence intervals

The `confint()` method returns the parameter-scale estimates (`phi`, `k0`, `k1`)
alongside the agreement-scale estimate.

```{r confint}
confint(fit)
```



## Item effects

The original data also contain TREC labels, which correspond to evaluations given by experts on a binary scale (relevant = 1 / non-relevant = 0). We can plot the estimated $\alpha$ vector to visualise how the model captured the different relevance levels across items

```{r item-effects, fig.width=6, fig.height=5}
doc_levels <- levels(factor(topic$document_id))
alphas <- coef(fit)[grep("^alpha", names(coef(fit)))]
trec <- tapply(topic$trec, topic$document_id, function(x) x[!is.na(x)][1])
boxplot(
  alphas ~ factor(trec[doc_levels]),
  xlab = "TREC", 
  ylab = "Item effect",
  col = c("#F28E2B", "#4E79A7"))
```

## Agreement across topics

```{r all-topics, fig.width=7, fig.height=5}
topics <- sort(unique(roitero2021$topic_id))
res <- do.call(rbind, lapply(topics, function(tid) {
  d <- subset(roitero2021, topic_id == tid)
  gw <- intersect(
    unique(d[d$relevance_score > 75 & d$gold == "H", ]$unit_id),
    unique(d[d$relevance_score < 25 & d$gold == "N", ]$unit_id)
  )
  d <- subset(d, unit_id %in% gw & gold == "null")
  ci <- confint(agreement(
    rating_data(d$relevance_score / 100, as.integer(factor(d$document_id)), VERBOSE = FALSE),
    NUISANCE = "items"
  ))$agreement
  c(agr = ci["agreement", "Estimate"], lo = ci["agreement", "2.5 %"], hi = ci["agreement", "97.5 %"])
}))

idx <- seq_along(topics)
plot(idx, res[, "agr"],
  ylim = range(res[, c("lo", "hi")]), xaxt = "n",
  xlab = "Topic", ylab = "Agreement", pch = 19,
  col = "#4E79A7", bty = "l")
axis(1, at = idx, labels = topics, las = 2)
segments(idx, res[, "lo"], idx, res[, "hi"], col = "#4E79A7")
```